Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828

### 2017-10-10 inst/examples/20160715-Krakow-Fennica.Rmd
manuscript figs added
sync

---
title: "Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828"
author: "Mikko Tolonen, Jani Marjanen, Hege Roivainen, Leo Lahti"
date: "`r Sys.Date()`"
output: 
  beamer_presentation:
    theme: "boxes"
    colortheme: "orchid"
    fonttheme: "professionalfonts"
fontsize: 13pt
---

>>>>

---
title: "Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828"
author: "Mikko Tolonen, Leo Lahti, Hege Roivainen, Jani Marjanen"
date: "`r Sys.Date()`"
output: 
  beamer_presentation:
    theme: "boxes"
    colortheme: "orchid"
    fonttheme: "professionalfonts"
fontsize: 13pt
---
